---
title       : Storm Database Explorer
subtitle    : 
author      : pvuppalapaty
job         : 
framework   : revealjs        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []           # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: libraries/nvd3}
mode        : selfcontained # {standalone, draft}
revealjs:
  theme: simple
---


## Storm Database Explorer


Welcome to Storm Database Explorer

This application is based on the U.S. National Oceanic and Atmospheric Administration's (NOAA) storm database.

You can adjust date range and event types using control panel located on the left side. Filtered dataset can be downloaded using data tab.

```{r, echo=FALSE}
library(data.table)
library(rCharts)
library(reshape2)
library(knitr)

dt <- fread('data/events.agg.csv')
dt.agg.year <- dt[, list(Count=sum(COUNT), Injuries=sum(INJURIES), Fatalities=sum(FATALITIES)), by=list(YEAR)]
```


--- .custom

## Between 1950 and 2011 severe weather events caused at least

 - `r format(sum(dt$FATALITIES), big.mark=' ')` deaths
 - `r format(sum(dt$INJURIES), big.mark=' ')` injuries
 - $`r format(round((sum(dt$PROPDMG) + sum(dt$CROPDMG)) / 1000), big.mark=' ')` billion worth of damage
 

--- .custom

## Now you can prepare yourself using Storm Database Explorer



 - state of the art user interface
 - high quality data
 - fast and reliable
 - 100% Open source 


--- .custom

## ... and it can generate cool plots


```{r nvd3plot2, results = 'asis', comment = NA, message = F, echo = F} 
require(rCharts)
require(knitr)
data <- melt(dt.agg.year[, list(YEAR=YEAR, Injuries=Injuries, Fatalities=Fatalities)], id='YEAR')
populationImpact <- nPlot(
    value ~ YEAR, group = 'variable', data = data[order(-YEAR, variable, decreasing = T)],
    type = 'stackedAreaChart', dom = 'populationImpact'
)
        
populationImpact$chart(margin = list(left = 100))
populationImpact$yAxis( axisLabel = "Affected", width = 80)
populationImpact$xAxis( axisLabel = "Year", width = 70)
        
populationImpact
```
        

--- .custom

## References

Shiny App  - https://pv1984.shinyapps.io/StormData/


Thank you!







